The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-30 Writeup/paper_v3.tex
identity / identify typo

COSMOS is a flux-limited survey and is therefore affected by Malmquist
bias, with the galaxy samples at higher redshift being intrinsically
brighter on average.  
Our analysis involves comparing galaxies in different redshift slices
to identity significant differences in morphology that arise due to
morphology-density correlations.  Such an analysis would be very
difficult with a flux-limited sample because there would be some
variation in morphology with redshift just due to the intrinsic change
in the sample properties.  For a fair comparison, we must restrict
ourselves to galaxies that are bright enough that they would be
observed at all redshifts that we consider, which is achieved by
volume-limiting the sample.  We consider three different ways of
carrying out this process, which results in three different galaxy
sample selections, all of which we will use in the remainder of the
analysis.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}

>>>>

COSMOS is a flux-limited survey and is therefore affected by Malmquist
bias, with the galaxy samples at higher redshift being intrinsically
brighter on average.  
Our analysis involves comparing galaxies in different redshift slices
to identify significant differences in morphology that arise due to
morphology-density correlations.  Such an analysis would be very
difficult with a flux-limited sample because there would be some
variation in morphology with redshift just due to the intrinsic change
in the sample properties.  For a fair comparison, we must restrict
ourselves to galaxies that are bright enough that they would be
observed at all redshifts that we consider, which is achieved by
volume-limiting the sample.  We consider three different ways of
carrying out this process, which results in three different galaxy
sample selections, all of which we will use in the remainder of the
analysis.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
